Novel Methods for Characterizing Peaks from Direct Injection FT-MS Experiments

### 2019-08-21 peakcharacterization_manuscript.Rmd
rsd table and the plot

```{r rsd_plots}
drake::loadd(rsd_plot_data)
rsd_plot_data
```

```{r rsd_table}
drake::loadd(rsd_table_data)
knitr::kable(rsd_table_data, digits = 3)
```

>>>>

```{r rsd_plots}
drake::loadd(rsd_plot_rsd_data)
rsd_plot_rsd_data
```

```{r rsd_table}
drake::loadd(rsd_table_rsd_data)
knitr::kable(rsd_table_rsd_data, digits = 3)
```
